A Meta-analysis of Longevity Estimates of Mosquito Vectors of Disease: Additional Methods

### 2020-11-14 writeUp/supplementary_materials_methods.tex
updated figures and added analysis navigator

For each individual series, we recorded the following meta-data: genus, species, collection method, whether or not insecticide was mentioned as being used during or shortly before the time of mosquito collections, and the start and end dates of the experiment. At the article level, we recorded the following meta-data: author, year, title, country, location (within country), start and end date, whether insecticide was used during any of the experimental replicates, whether an MRR experiment occurred alongside the dissection study, and the collection location (indoor or outdoor). At either the individual series or article levels, we recorded additional meta-data describing the nature of data collection, for example explaining where the data was contained within the article, whether it was obtained by digitising graphs, and the number of separate dated series. For those few cases ($n=16$ series) where the data was obtained by digitising graphs, we used the WebPlotDigitizer online tool \citep{digitise}.

@@

\subsection{Model estimation by MCMC and cross validation}
The statistical models were fit to data using Stan's NUTS algorithm \cite{carpenter2016stan}. In all cases, models were run for 1000 iterations on each of 12 chains, with the first half of the iterations discarded as warm-up. We monitored diagnosed convergence as per \cite{gelman1992inference}, with $\hat{R}<1.1$ on all parameters. In all model runs, there were fewer than a handful of divergent transitions.

@@

The folds were chosen so that, at all levels of analysis, there was always at least a handful of data points belonging to a particular group in the training set. This meant that, to generate meaningful comparisons between the species-level, complex-level and continent-level models, we selected only those data points with at least 5 observations for each species and complex. This reduced the number of data points used for model comparison versus those used for model estimation. For Africa, we had $n=223$ data points; for the Americas, there were $n=141$; and for Asia, there were $n=214$.

For the comparison between continent-level grouping and overall, we were able to use more data points since we were less constrained by the minimal numbers of data belonging to each group. This meant we had $n=1490$ data points, with $n=778$ for Africa, $n=163$ for the Americas, and $n=549$, for Asia.

>>>>

For each individual series, we recorded the following meta-data: genus, species, collection method and the start and end dates of the experiment. At the article level, we recorded the following meta-data: author, year, title, country, location (within country), start and end date, whether an MRR experiment occurred alongside the dissection study, and the collection location (indoor or outdoor). At either the individual series or article levels, we recorded additional meta-data describing the nature of data collection, for example explaining where the data was contained within the article, whether it was obtained by digitising graphs, and the number of separate dated series. For those few cases ($n=16$ series) where the data was obtained by digitising graphs, we used the WebPlotDigitizer online tool \citep{digitise}.

@@

\subsection{Model estimation by MCMC and cross validation}
The statistical models were fit to data using Stan's NUTS algorithm \cite{carpenter2016stan}. In all cases, models were run for 4000 iterations on each of 12 chains, with the first half of the iterations discarded as warm-up. We monitored diagnosed convergence as per \cite{gelman1992inference}, with $\hat{R}<1.1$ on all parameters. In all model runs, there were fewer than a handful of divergent transitions.

@@

The folds were chosen so that, at all levels of analysis, there was always at least a handful of data points belonging to a particular group in the training set. This meant that, to generate meaningful comparisons between the species-level, complex-level and continent-level models, we selected only those data points with at least 5 observations for each species and complex. This reduced the number of data points used for model comparison versus those used for model estimation. For Africa, we had $n=217$ data points; for the Americas, there were $n=107$; and for Asia, there were $n=108$.

For the comparison between continent-level grouping and overall, we were able to use more data points since we were less constrained by the minimal numbers of data belonging to each group. This meant we had $n=1126$ data points, with $n=679$ for Africa, $n=126$ for the Americas, and $n=321$, for Asia.
